Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-11-13 paper/appendix.tex
fix
o

\subsection{Robustness on increasing number of factors}

To test whether each of the methods robustly scale to an increasingly large number of potential causes $X$, we enhance the four ad-hoc features (word length, word frequency, word function, dummy variable) with another ten features. These additional features corresponds to the first dimensions of word embedding as provided by Spacy \citep{spacy2}. The results shown in Figure \ref{fig:embbeding}, show that the ad-hoc features remain unchanged (and are actually improved) in the B2B.

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figures/compare_embeddings.pdf}
  \caption{Comparison of $\Delta R$ when the models are tested on four variables (top) and when the models are tested on an these four variables as well as another 10 word-embedding features (bottom). These results illustrate that, unlike Regularized CCA, B2B remains robust even when the number of tested factors increases.
  \label{fig:embeddings}}
\end{figure}

>>>>

\subsection{Robustness to increasing number of factors}

To test whether each of the methods robustly scales to an increasingly large number of potential causes $X$, we enhanced the four ad-hoc features (word length, word frequency, word function, dummy variable) with another ten features. These additional features corresponds to the first dimensions of word embedding as provided by Spacy \citep{spacy2}. The results shown in Figure \ref{fig:embbedings}, show that the feature importance of ad-hoc features as derived by B2B remain unchanged (and are actually improved).

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/compare_embeddings.pdf}
  \caption{Comparison of $\Delta R$ when the models are tested on four variables (top) and when the models are tested on an these four variables as well as another 10 word-embedding features (bottom). These results illustrate that, unlike Regularized CCA, B2B remains robust even when the number of tested factors increases.
  \label{fig:embeddings}}
\end{figure}

### 2019-11-13 paper/introduction.tex
o

The present paper focuses on the restricted issue of disentangling the causal influence of linearly correlated predictors ($X$) onto multivariate observations ($Y$). This issue thus differs from other causal discovery algorithms based on temporal-delays and/or nonlinear interaction in systems where the directionality of causation (from X to Y or vice versa) is unknown (e.g. \citep{peters2017elements, granger1969investigating, janzing2013quantifying, scholkopf2016modeling}.

>>>>

The present paper focuses on the restricted issue of disentangling the causal influence of linearly correlated predictors ($X$) onto noisy multivariate observations ($Y$). The present approach thus differs from other causal discovery algorithms based on temporal-delays and/or nonlinear interaction in systems where the directionality of causation (from X to Y or vice versa) is unknown (e.g. \citep{peters2017elements, granger1969investigating, janzing2013quantifying, scholkopf2016modeling}.
